Field-informed Reinforcement Learning for Learning Large-Scale Collective Tasks

### 2023-05-11 paper.tex
minor: add hypen in large-scale

\usepackage{cleveref}
\lstset{language=Pascal}
\begin{document}
%
\title{Field-informed Reinforcement Learning for Learning Large Scale Collective Tasks} %% Todo improve
% or: Field-Informed Reinforcement Learning: A Scalable and Effective Method for Collective Intelligence
% or: A Novel Approach to Reinforcement Learning for Adaptive Collective Systems
%

@@

Examples of such large scale system can be a network of robots (e.g., swarm robotics), camera and IoT networks, or a network of mobile phones.

>>>>

\usepackage{cleveref}
\lstset{language=Pascal}
\begin{document}
%
\title{Field-informed Reinforcement Learning for Learning Large-Scale Collective Tasks} %% Todo improve
% or: Field-Informed Reinforcement Learning: A Scalable and Effective Method for Collective Intelligence
% or: A Novel Approach to Reinforcement Learning for Adaptive Collective Systems
%

@@

Examples of such large-scale system can be a network of robots (e.g., swarm robotics), camera and IoT networks, or a network of mobile phones.
